A Survey on Ordered Binary Decision Diagrams

### 2015-09-14 paper.tex
Add OBDD representation for Symbolic model checking

The main idea behind this approach is to represent the state space symbolically,
instead of explicitly with e.g. a state table. Such explicit state tables may grow
exponentially with the number of concurrent components, because the state space
does so. Commonly, this is referred to as the
\textit{state explosion problem}~\cite{BURCH90, MCMILLAN92}. \tbr

>>>>

The main idea behind this approach is to represent the state space symbolically,
instead of explicitly with e.g. a state table. Such explicit state tables may grow
exponentially with the number of concurrent components, because the state space
does so. Commonly, this is referred to as the
\textit{state explosion problem}~\cite{BURCH90, MCMILLAN92}. To overcome this
problem, Burch et al.~\cite{BURCH90} as well as McMillan~\cite{MCMILLAN92}
proposed to utilize reduced ordered binary decision diagrams to represent the 
state space symbolically. Although OBDDs cannot avoid a state explosion in general,
many practically relevant systemes with large state spaces can be
verified~\cite{BURCH90, MCMILLAN92}. Experiments~\cite{BURCH90} showed that
symbolic model checking enables to verify models with more than $10^{20}$ states,
whereas explicit enumeration approaches can only verify models up to $10^6$
states.

Burch et al.~\cite{BURCH90} and McMillan~\cite{MCMILLAN92} extend Bryant's OBDD
representation~\cite{BRYANT86} by quantification over Boolean variables (QBF) and
substitution of variable names. The quantification over Boolean variables is
realized by using Bryant's \textit{Restrict} operation (see
Section~\ref{sec:operations}). Let $f$ be a QBF formula and $x$ be a Boolean
variable. The QBF formula $\exists x\left(f\right)$ then is equivalent to
$f|_{a=0} \lor f|_{a=1}$~\cite{BURCH90}. Substitution of variables, e.g.
substitute $x$ by $y$ (denoted $f\langle x\leftarrow y\rangle$), is computed using
the following equivalence:
\begin{center}
$
f\langle x\leftarrow y\rangle \equiv
\exists x\lbrack\left(x \Leftrightarrow y\right) \land f\rbrack
$
\end{center}
\tbr
